The Migration of the Field Code

### 2016-02-19 index.Rmd
Rename working paper

This is an analysis notebook for detecting text reuse in legal codes of civil procedure---the "Field codes"---in the nineteenth-century United States. It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com). This [working paper](talks/dh-working-group/dh-working-group.pdf) has the most up-to-date summary of what we are doing.

@@

- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/dh-working-group.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)

>>>>

This is an analysis notebook for detecting text reuse in legal codes of civil procedure---the "Field codes"---in the nineteenth-century United States. It is a collaboration between [Kellen Funk](http://kellenfunk.org/) and [Lincoln Mullen](http://lincolnmullen.com). This [working paper](talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.pdf) has the most up-to-date summary of what we are doing.

@@

- [AHA 2016 lightening talk slides](talks/aha2016/aha2016.html)
- Digital Humanities Working Group, George Mason University: [paper](talks/dh-working-group/Funk-Mullen.Migration-Field-Code.working-paper.pdf), [slides](talks/dh-working-group-slides/dh-working-group-slides.html)
